\part{\txt{参考文献，その他}{Bibliography and other documents}}
\label{part:bib}
% \bibliographystyle{plain}
% \bibliography{/home/ohori/work/bib/bibdb.bib}
\begin{thebibliography}{10}

\bibitem{bune96tods}
P.~Buneman and A.~Ohori.
\newblock Polymorphism and type inference in database programming.
\newblock {\em ACM Transactions on Database Systems}, 21(1):30--74, 1996.

\bibitem{gord79}
M.J. Gordon, A.J.R.G. Milner, and C.P. Wadsworth.
\newblock {\em Edinburgh {LCF}: A Mechanized Logic of Computation}.
\newblock Lecture Note in Computer Science. Springer-Verlag, 1979.

\bibitem{Kenah:1984:VID:225}
Lawrence~J. Kenah and Simon~F. Bate.
\newblock {\em VAX/VMS internals and data structures}.
\newblock Digital Press, Newton, MA, USA, 1984.

\bibitem{sml}
R.~Milner, M.~Tofte, and R.~Harper.
\newblock {\em The Definition of {Standard ML}}.
\newblock The MIT Press, 1990.

\bibitem{sml97}
R.~Milner, R.~Tofte, M.~Harper, and D.~MacQueen.
\newblock {\em The Definition of {Standard ML}}.
\newblock The MIT Press, revised edition, 1997.

\bibitem{nguyen06ppdp}
H-D. Nguyen and A.~Ohori.
\newblock Compiling ml polymporphism with explicit layout bitmap.
\newblock In {\em Proceedings of ACM Conference on Principles and Practice of
  Declarative Programming}, pages 237--248, 2006.

\bibitem{ohor92popl}
A~Ohori.
\newblock A compilation method for {ML}-style polymorphic record calculi.
\newblock In {\em Proceedings of ACM Symposium on Principles of Programming
  Languages}, pages 154--165, 1992.

\bibitem{ohor95toplas}
A.~Ohori.
\newblock A polymorphic record calculus and its compilation.
\newblock {\em ACM Transactions on Programming Languages and Systems},
  17(6):844--895, 1995.
\newblock A preliminary summary appeared at ACM POPL, 1992 under the title ``A
  compilation method for ML-style polymorphic record calculi''.

\bibitem{ohor88lfp}
A.~Ohori and P.~Buneman.
\newblock Type inference in a database programming language.
\newblock In {\em Proc. ACM Conference on LISP and Functional Programming},
  pages 174--183, Snowbird, Utah, July 1988.

\bibitem{ohor89sigmod}
A.~Ohori, P.~Buneman, and V.~Breazu-Tannen.
\newblock Database programming in {Machiavelli} -- a polymorphic language with
  static type inference.
\newblock In {\em Proc.\ the ACM SIGMOD conference}, pages 46--57, Portland,
  Oregon, May -- June 1989.

\bibitem{ohor07popl}
A~Ohori and I.~Sasano.
\newblock Lightweight fusion by fixed point promotion.
\newblock In {\em Proceedings of ACM Symposium on Principles of Programming
  Languages}, pages 143--154, 2007.

\bibitem{ohor97unbox}
A.~Ohori and T.~Takamizawa.
\newblock A polymorphic unboxed calculus as an abstract machine for polymorphic
  languages.
\newblock {\em J. Lisp and Symbolic Comput.}, 10(1):61--91, 1997.

\bibitem{ohori11}
A.~Ohori and K.~Ueno.
\newblock Making {Standard ML} a practical database programming language.
\newblock In {\em Proceedings of the ACM International Conference on Functional
  Programming}, pages 307--319, 2011.

\bibitem{ohor99icfp}
A.~Ohori and N.~Yoshida.
\newblock Type inference with rank 1 polymorphism for type-directed compilation
  of {ML}.
\newblock In {\em Proc.\ ACM International Conference on Functional
  Programming}, pages 160--171, 1999.

\bibitem{ueno11icfp}
K.~Ueno, A~Ohori, and T.~Otomo.
\newblock An efficient non-moving garbage collector for functional languages.
\newblock In {\em Proceedings of the ACM International Conference on Functional
  Programming}, 2011.
\newblock To appear.

\bibitem{ohori00sml}
大堀 淳.
\newblock {\em プログラミング言語Standard ML入門}.
\newblock 共立出版, 2000.

\end{thebibliography}
